---
title: "Homework 5"
author: Suhani Patel 
date: 2021-11-11
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    theme: yeti
    highlight: haddock
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, results = FALSE) 
```

```{r}
library(tidyverse)
library(stringr)
```

```{r}
homocide = read_csv(file = "./data/homicide-data.csv", na = c("", "Unknown")) #changes unknown to NA
```

# Problem 1

### Description of Dataset 
* The Homocide dataset includes `r length(homocide)` variables: `r variable.names(homocide)`.
* The dataset has `r nrow(homocide)` rows and `r ncol(homocide)` columns.
* The number of homocides in the dataset is `r count(homocide)`.

### Total Homcides
```{r}
homocide = 
  read_csv(file = "./data/homicide-data.csv", na = c("", "Unknown")) %>%  #changes unknown to NA
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest"     ~ "unsolved",
           disposition == "Open/No arrest"            ~ "unsolved",
           disposition == "Closed by arrest"          ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

### Proportions of Homocides in Baltimore
```{r}
baltimore_df = homocide %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n())

baltimore_test = prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

### Proportions of Homocides all Cities
```{r}
prop_test_function = function(city_df) {
  
  city_summary = city_df %>% 
    summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n())

  city_test = prop.test(
    x = city_summary %>% pull(unsolved),
    n = city_summary %>% pull(n))

return(city_test)

}

prop_test_function(baltimore_df)
```

```{r}
results_df = homocide %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

### Plot
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
  
******

# Problem 2

### Tidying
```{r}
dataframe = tibble(files = list.files("data/zip_data/")) %>% 
  mutate(
    path_name = paste0("./data/zip_data/", files),
    data = map(.x = path_name, ~read_csv(.x))) %>% 
  mutate(files = str_replace(files, ".csv", "")) %>% 
  unnest(data) %>% 
  select(-path_name) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "data") %>% 
  separate(week, into = c("week1", "week"), sep = "_") %>% 
  select(-week1) %>% 
  mutate(week = as.numeric(week)) %>% 
  mutate(group = files) %>% 
  separate(group, into = c("group", "ID"), sep = "_") %>% 
  select(-"ID") %>% 
  mutate(group = ifelse(group == "con", "Experimental", "Control")) 
```

### Plot 

```{r}
plot = dataframe %>% 
  group_by(files) %>%  
  ggplot(aes(x = week, y = data, color = group)) +
  geom_point(alpha = .6) + geom_path() +
  labs(
    title = "Data Values over Time in each Experimental Group",
    x = "Week",
    y = "Data value",
    color = "group") + 
  theme(legend.position = "bottom")

plot
```

The experimental group has lower data values than the control group as time goes on. The control group has increasing data values over time while the experimental group has decreasing data values over time. 

******

# Problem 3

### Importing
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

### Function
```{r}
fill_in_missing = function(x) {
  
  if (typeof(x) == "character") 
  {x[is.na(x)]="virginica"}
  
  else 
  {x[is.na(x)]= mean(x, na.rm = TRUE) }
  
  return(x)
  
  }
```

### Mapping 

```{r}
output = map(iris_with_missing, fill_in_missing) 
```

